A Large and Variable Leading Tail of Helium in a Hot Saturn Undergoing Runaway Inflation

### 2023-08-10 paper/paper1/ms.tex
referee comment 5-- summary and ms edits

Finally, we consider the prospect that the planetary mass of HAT-P67b is much lower than the 1-$\sigma$ estimate, such that the white-light planetary radius \emph{is} the Hill radius (we have previously assumed the Hill radius is 2.7 planetary radii).  This extreme scenario could manifest enormous mass loss rates, with the atmosphere's reservoir of mass fleeing the gravitational potential well directly, without the cushion of an exosphere.  This terminal Roche Lobe overflow should have observational consequences.  In particular, heavy elements would easily leak into the planetary wind, yielding possibly many observable metal lines in the UV.

>>>>

Finally, we consider the prospect that the planetary mass of HAT-P67b is much lower than the 1-$\sigma$ estimate, such that the white-light planetary radius \emph{is} the Hill radius (we have previously assumed the Hill radius is 2.7 planetary radii).  This \edit1{true Roche Lobe Overflow (RLO)} scenario could manifest enormous mass loss rates, with the atmosphere's reservoir of mass fleeing the gravitational potential well directly, without the cushion of an exosphere.  \edit1{We propose that this terminal RLO should have a subtle-but-distinctive observational consequence.  Since heavy elements have smaller scale heights than hydrogen/helium, the observed ratio of heavy element to lighter element lines should be inversely correlated with the number of scale heights separating the white-light radius from the Hill radius.  All else equal, we would expect an anomalously large ratio of heavy metals compared to hydogen/Helium in the RLO case.  The extremely large Helium excess absorption, combined with the possibility of enhanced metal line depths in HAT-P-67~b---however uncertain---motivates a search for metal-line spectral tracers that may have previously been dismissed as too unlikely to detect.}

\edit1{Establishing the scale of this metal enhancement would be difficult.  First, XUV-driven mass loss would also carry away metals in the upper atmosphere, and so careful modeling would have to be established to predict what enhancement could be reasonably expected.  Second, few exoplanets currently have multiple atmospheric escape tracers measured, so a purely observational detection would be challenging, not to mention needing to account for metallicity.  Eventually such a phenomenon may be possible as our inventory of systems grows and our measurement precisions improve.  A direct mass measurement via improved RV precision would be a more direct way way to establish whether HAT-P-67~b is truly in a Roche Lobe Overflow scenario.}
